---
title: false
output: word_document
date: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(flextable)
```

```{r echo=FALSE}

datasets <- readr::read_csv("cap_datasets.csv") |>
  dplyr::mutate(
    ordering = stringr::str_extract(package, "[0-9]+"),
    ordering = as.integer(ordering)
    ) |>
  dplyr::arrange(ordering) |>
  dplyr::select(
    `dataset id`       = package,
    `dataset citation` = citation,
    `CRA`              = core_area
  )

```

### Supplementary Document: List of datasets deposited into the EDI

CAP LTER datasets available through the Environmental Data Initiative (EDI) data repository. Table columns include a) the EDI Data Package Identifier; b) dataset citation, including dataset creator(s), year of (most recent) publication to EDI, title, current version, and DOI; and c) associated Core Research Area(s): PP=primary production, PC=population/community dynamics, ND=nutrient dynamics, OM=organic matter dynamics, D=disturbance, LU=land use/land cover change, SES=social-ecological systems dynamics. Datasets that have contributed to CAP's Top Ten publications (see II. Intellectual Merit: Results of Prior Support) are highlighted.

```{r flextable, echo=FALSE}

table_caption <- "CAP LTER datasets available through the Environmental Data Initiative (EDI) data repository. Table columns include a) the EDI Data Package Identifier; b) dataset citation, including dataset creator(s), year of (most recent) publication to EDI, title, current version, and DOI; and c) associated Core Research Area(s): PP=primary production, PC=population/community dynamics, ND=nutrient dynamics, OM=organic matter dynamics, D=disturbance, LU=land use/land cover change, SES=social-ecological systems dynamics. Datasets that have contributed to CAP's Top Ten publications (see II. Intellectual Merit: Results of Prior Support) are highlighted."

datasets |>
  flextable() |>
  align(part = "all") |> # left align
  # set_caption(
  #   caption = table_caption,
  #   style = "Table Caption"
  #   ) |>
  font(fontname = "Arial (Body)", part = "all") |>
  fontsize(size = 10, part = "all") |>
  # set_table_properties(layout = "autofit", width = 1) |>
  width(j = c(1,2,3), width = c(1.8,5,1)) |>
  valign(valign = "top", part = "body") |>
  # highlight top ten
  bg(
    i = grepl(
      pattern = "\\.46\\.|\\.650\\.|\\.667\\.|\\.630\\.|\\.633\\.|\\.278\\.|\\.652\\.|\\.642\\.|\\.560\\.|\\.631\\.|\\.632\\.",
      x = datasets$`dataset id`,
      ignore.case = TRUE
      ),
    j = c(1, 2, 3),
    bg = "wheat",
    part = "body"
    )
```
